### 2020-12-01 README.Rmd
updated README to show that the article is published in Ecosphere
updated the README to have the correct title

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models"
Authors <- "See, Kevin E., Michael W. Ackerman, Richard A. Carmichael, Sarah Hoffman, and Chris Beasley"
yr <- 2020
Journal <- "Ecological Modelling"
```

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"
Authors <- "See, Kevin E., Michael W. Ackerman, Richard A. Carmichael, Sarah Hoffman, and Chris Beasley"
yr <- 2020
Journal <- "Ecosphere"
```
